Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-03-24 main.Rmd
linear  granularities relativities revised

If ${S_0,\dots,S_{R-1}}$ are the sets of indexes of $G$ describing
$H(0), \dots, H(R - 1)$, respectively, then the description of an arbitrary granule $H(j)$ is given by $\bigcup_{i \in S_j \mod R}G(P*\lfloor j/R \rfloor + i)$. Also, granularities can be periodical with respect to other granularities, except for a finite number of spans of time where they behave in an anomalous way [@Bettini2000-vy]. These are called quasi-periodic relationships.

@@

For example, in a Gregorian calendar without leap years we could say days group periodically into months with the period $P = 365$ and the number of granules of "months" in each period given by $R=12$. In a Gregorian calendar with leap years, days group quasi-periodically into months with the <!--The value of $P$ and $R$ would still be 365 and 12 respectively, while the $E_i$s--> exceptions of the time domain corresponding to $29^{\text{th}}$ February of any year.

@@

A discrete time model often uses a fixed smallest linear granularity named by @Bettini1998-ed _bottom granularity_.  <!--so that the the underlying time domain can be described as a sequence of non-decomposable, consecutive time intervals of some fixed, minimal duration called _chronons_ (@Jensen1998-qn). Chronons may be grouped into granules of a bottom granularity and --> Granules in bottom granularity or any finer granularity may be aggregated in some manner to form larger granules belonging to a coarser granularity. A system of multiple granularities in lattice structures is referred to as a _calendar_ by @Dyreson2000-mr.

>>>>

If ${S_0,\dots,S_{R-1}}$ are the sets of indexes of $G$ describing
$H(0), \dots, H(R - 1)$, respectively, then the description of an arbitrary granule $H(j)$ is given by $\bigcup_{i \in S_j \mod R}G(P*\lfloor j/R \rfloor + i)$. Also, granularities can be periodical with respect to other granularities, except for a finite number of spans of time where they behave in an anomalous way, called **quasi-periodic** relationships by @Bettini2000-vy.

@@

\noindent For example, in a Gregorian calendar without leap years we could say days group periodically into months with the period $P = 365$ and the number of granules of "months" in each period given by $R=12$. In a Gregorian calendar with leap years, days group quasi-periodically into months with the <!--The value of $P$ and $R$ would still be 365 and 12 respectively, while the $E_i$s--> exceptions of the time domain corresponding to $29^{\text{th}}$ February of any year.

@@

A discrete time model often uses a fixed smallest linear granularity named by @Bettini1998-ed **bottom granularity**.  <!--so that the the underlying time domain can be described as a sequence of non-decomposable, consecutive time intervals of some fixed, minimal duration called _chronons_ (@Jensen1998-qn). Chronons may be grouped into granules of a bottom granularity and --> Granules in bottom granularity or any finer granularity may be aggregated in some manner to form larger granules belonging to a coarser granularity. A system of multiple granularities in lattice structures is referred to as a **calendar** by @Dyreson2000-mr.
